### 2018-07-25 chapters/01-introduction/intro.tex
Clear unused files, upload highres images and fix errors

Translations from generic \LaTeX{} to \gls{cas} are difficult to realize since the semantic information are not explicitely given in the input. The \gls{nist} has created a set of semantic \LaTeX{} macros~\cite{DLMF:Macros}. Each macro ties specific character sequences to a well-defined mathematical object and is linked with the corresponding definition in the \gls{dlmf} or \gls{drmf}. These macros embeds necessary semantic information into \LaTeX{} expressions. One example of such a macro is given table~\ref{tab:JacobiP-usecase} for the semantic \LaTeX{} representation for the Jacobi polynomial. The macros provide isolated access to important parts of the mathematical function, such as the arguments.

Even with embedded semantic information, a translation between the systems can be difficult. A typical example of complex problems occurs for multivalued functions~\parencite{AISC:MultivaluedFunctions}. A \gls*{cas} usually defines \textit{branch cuts} to compute principal values of multivalued functions~\parencite{Maple:Cuts}, which makes the implementation of a theoretically continues function to a discontinued presentation of it. In general, positioning branch cuts follows conventions, but can be positioned arbitrarily in many cases. Communicate and explain the decision of defined branch cuts is a critical point for \gls{cas} and can vary between the systems~\parencite{Branches:acot}. Figure~\ref{fig:acot-cut-compare} illustrates two examples of different branch cut positioning for the inverse trigonometric arccotangent function. While \Maple{} defines the branch cut at ${[-\infty\iunit, -\iunit]}$, ${[\iunit,\infty\iunit]}$ (figure~\ref{fig:acot-cut1}), \Mathematica{} defines the branch cut at ${[-\iunit, \iunit]}$ (figure~\ref{fig:acot-cut2}).

@@

This article presents a new approach for automatic \gls{p2c} and vice versa conversions. Translations from presentational to computational (computational to presentational) systems are called forward (backward) translations. A forward translation is denoted with an arrow with the target system language above the arrow. For example,
\begin{equation*}
t \overset{\langMaple}{\mapsto} c,
\end{equation*}
where $t$ is an expression in the \LaTeX{} language and $c$ is an element of the \Maple{} language $\langMaple$. As we will see later in this article, we need to compare mathematical concepts between systems. This is impossible from a mathematical point of view. Consider the irrational mathematical constant $e$, known as Euler's number. The theoretical construct for this symbol cannot be mathematically equivalent to the value \verb|exp(0)| in \Maple, caused by computational and implementational limitations. Instead of using the term \textit{equivalent}, we introduce a \textit{appropriate} and \textit{inappropriate} translations. We call a translation such as
\begin{equation}\label{eq:cos-def}
\verb|\cos@{z}| \overset{\langMaple}{\mapsto} \verb|cos(z)|
\end{equation}
as \textit{appropriate}, while a translation such as
\begin{equation}
\verb|\cos@{z}| \overset{\langMaple}{\mapsto} \verb|sin(z)|
\end{equation}
is called \textit{inappropriate}. Note that it is not always as easy as in this example to decide if a translation is appropriate or not. Therefore, this article also presents several validation techniques to automatically verify if a translation is appropriate or inappropriate. In addition to this terminology, we introduce \textit{direct translations}. Later in the paper, we will explain that a translation from one specific mathematical object to its \textit{appropriate} counterpart in the other system is not always possible. We call a translation to the \textit{appropriate} counterpart \textit{direct}. For example, the translation~(\ref{eq:cos-def}) is \textit{direct}, while a translation to the definition of the cosine function
\begin{equation*}
\verb|\cos@{z}| \overset{\langMaple}{\mapsto} \verb|(exp(I*z)+exp(-I*z))/2|
\end{equation*}
is not a \textit{direct} translation.

>>>>

Translations from generic \LaTeX{} to \gls*{cas} are difficult to realize since the semantic information are not explicitely given in the input. The \gls*{nist} has created a set of semantic \LaTeX{} macros~\cite{DLMF:Macros}. Each macro ties specific character sequences to a well-defined mathematical object and is linked with the corresponding definition in the \gls*{dlmf} or \gls*{drmf}. These macros embeds necessary semantic information into \LaTeX{} expressions. One example of such a macro is given table~\ref{tab:JacobiP-usecase} for the semantic \LaTeX{} representation for the Jacobi polynomial. The macros provide isolated access to important parts of the mathematical function, such as the arguments.

Even with embedded semantic information, a translation between the systems can be difficult. A typical example of complex problems occurs for multivalued functions~\parencite{AISC:MultivaluedFunctions}. A \gls*{cas} usually defines \textit{branch cuts} to compute principal values of multivalued functions~\parencite{Maple:Cuts}, which makes the implementation of a theoretically continues function to a discontinued presentation of it. In general, positioning branch cuts follows conventions, but can be positioned arbitrarily in many cases. Communicate and explain the decision of defined branch cuts is a critical point for \gls*{cas} and can vary between the systems~\parencite{Branches:acot}. Figure~\ref{fig:acot-cut-compare} illustrates two examples of different branch cut positioning for the inverse trigonometric arccotangent function. While \Maple{} defines the branch cut at ${[-\infty\iunit, -\iunit]}$, ${[\iunit,\infty\iunit]}$ (figure~\ref{fig:acot-cut1}), \Mathematica{} defines the branch cut at ${[-\iunit, \iunit]}$ (figure~\ref{fig:acot-cut2}).

@@

This article presents a new approach for automatic \gls*{p2c} and vice versa conversions. Translations from presentational to computational (computational to presentational) systems are called forward (backward) translations. A forward translation is denoted with an arrow with the target system language above the arrow. For example,
\begin{equation*}
t \overset{\langMaple}{\mapsto} c,
\end{equation*}
where $t$ is an expression in the \LaTeX{} language and $c$ is an element of the \Maple{} language $\langMaple$. As we will see later in this article, we need to compare mathematical concepts between systems. This is impossible from a mathematical point of view. Consider the irrational mathematical constant $e$, known as Euler's number. The theoretical construct for this symbol cannot be mathematically equivalent to the value \verb|exp(0)| in \Maple, caused by computational and implementational limitations. Instead of using the term \textit{equivalent}, we introduce a \textit{appropriate} and \textit{inappropriate} translations. We call a translation such as
\begin{equation}\label{eq:cos-def}
\verb|\cos@{z}| \overset{\langMaple}{\mapsto} \verb|cos(z)|
\end{equation}
as \textit{appropriate}, while a translation such as
\begin{equation}
\verb|\cos@{z}| \overset{\langMaple}{\mapsto} \verb|sin(z)|
\end{equation}
is called \textit{inappropriate}. Note that it is not always as easy as in this example to decide if a translation is appropriate or not. Therefore, this article also presents several validation techniques to automatically verify if a translation is appropriate or inappropriate. In addition to this terminology, we introduce \textit{direct translations}. Later in the paper, we will explain that a translation from one specific mathematical object to its \textit{appropriate} counterpart in the other system is not always possible. We call a translation to the \textit{appropriate} counterpart \textit{direct}. For example, the translation~(\ref{eq:cos-def}) is \textit{direct}, while a translation to the definition of the cosine function
\begin{equation*}
\verb|\cos@{z}| \overset{\langMaple}{\mapsto} \verb|(exp(I*z)+exp(-I*z))/2|
\end{equation*}
is not a \textit{direct} translation.

### 2018-07-25 chapters/03-translator/backward-trans.tex
Clear unused files, upload highres images and fix errors

\begin{wrapfigure}{r}{0.62\textwidth}
	\vspace{-22pt}
	\centering
	\includegraphics[clip, trim=0.1cm 0.1cm 0.1cm 0.1cm, scale=0.5]{DAGreal.pdf}
	\vspace{-26pt}
	\caption{The internal \Maple{} DAG representation of $x^2+x$.}
	\label{fig:internal-maple-dag}
	\vspace{-15pt}
\end{wrapfigure}

@@

\Maple{} evaluates inputs automatically and changes the input into an internal representation. This internal representation might look a bit different to the input. One example has already been given with figure~\ref{internal-maple-dag}, where each summand of a sum is stored with a factor. Here is a list of all internal changes that occur for inputs.

>>>>

\begin{wrapfigure}{r}{0.61\textwidth}
	\vspace{-22pt}
	\centering
	\includegraphics[clip, trim=0.5cm 0.5cm 0.5cm 0.5cm, scale=0.5]{DAGreal.pdf}
	\vspace{-5pt}
	\caption{The internal \Maple{} DAG representation of $x^2+x$.}
	\label{fig:internal-maple-dag}
	\vspace{-15pt}
\end{wrapfigure}

@@

\Maple{} evaluates inputs automatically and changes the input into an internal representation. This internal representation might look a bit different to the input. One example has already been given with figure~\ref{fig:internal-maple-dag}, where each summand of a sum is stored with a factor. Here is a list of all internal changes that occur for inputs.

### 2018-07-25 chapters/03-translator/forward-trans.tex
Clear unused files, upload highres images and fix errors

The overall forward translation process is explained in figure~\ref{fig:forward-trans}. All translation patterns and related information are stored in the DLMF/DRMF tables. These tables are converted by the \verb|lexicon-creator.jar| to the \verb|DLMF-macros-lexicon.txt| lexicon file. Together with the \verb|global-lexicon.txt| file, the \gls*{pom-pt} will be created by the \gls*{pom}-tagger. The \verb|latex-converter.jar| takes a string representation of a semantic \LaTeX{} expression and uses the \gls*{pom} engine as well as our \verb|Translator| to create an appropriate string representation for a specified \gls*{cas}.

>>>>

{\sloppy The overall forward translation process is explained in figure~\ref{fig:forward-trans}. All translation patterns and related information are stored in the DLMF/DRMF tables. These tables are converted by the \verb|lexicon-creator| to the \verb|DLMF-macros-lexicon| lexicon file. Together with the \verb|global|-\verb|lexicon| file, the \gls*{pom-pt} will be created by the \gls*{pom}-tagger. The \verb|latex-converter| takes a string representation of a semantic \LaTeX{} expression and uses the \gls*{pom} engine as well as our \verb|Translator| to create an appropriate string representation for a specified \gls*{cas}.}
